---
title: "Code and Analysis for Siri"
date: "2022-12-11"
output: github_document
---

```{r libraries set up, message = FALSE}
library(tidyverse)
library(ggplot2)
library(patchwork)
library(GGally)
library(leaps)
library(caret)
```

```{r dataset set up}
bodyfat_df = 
  readxl::read_excel("body_density_data.xlsx") %>%
  janitor::clean_names() 

head(bodyfat_df)
```

## Exploratory Analysis and Transformations

```{r Y distribution exploration}
par(mfrow=c(1,3))

boxplot(bodyfat_df$bodyfat_brozek, main='bodyfat_brozek')
boxplot(bodyfat_df$bodyfat_siri, main='bodyfat_siri')
boxplot(bodyfat_df$body_density, main='bodyfat_density')

brozek = 
bodyfat_df %>%
  ggplot(aes(x = bodyfat_brozek)) +
  geom_histogram()

siri = 
bodyfat_df %>%
  ggplot(aes(x = bodyfat_siri)) +
  geom_histogram()

density =
bodyfat_df %>%
  ggplot(aes(x = body_density)) +
  geom_histogram()

brozek + siri + density
```

NOTE: All are approximately normal
* Probably going with Brozek. (60-92)

```{r checking validity in y choice}
bodyfat_df %>%
  ggplot(aes(x = age)) +
  geom_histogram()
```

```{r descriptive stats of variables}
bodyfat_df %>% 
  select(-id, -bodyfat_brozek, -body_density) %>% 
  gtsummary::tbl_summary() %>% 
  gtsummary::bold_labels()
```

```{r normality, y-x rels, collinearity in covariates (xs)}
bodyfat_df %>% 
  select(-bodyfat_brozek, -body_density, -id) %>% 
  relocate("bodyfat_siri") %>% 
  ggpairs()
```

```{r inv_transformation for weight}
before = 
bodyfat_df %>%
  ggplot(aes(x = weight)) +
  geom_density()

after = 
bodyfat_df %>% 
  mutate(inv_weight = 1/(weight)) %>% 
  ggplot(aes(x = inv_weight)) +
  geom_density()

before + after
```

NOTE: For the almost normal but right skewed distributions, inverse transformation is making a considerable difference. From this point, inversely transforming (weight and neck --- bicep). 

```{r inverse transforms}
bodyfat_df = 
  bodyfat_df %>%
  mutate(i_weight = 1/weight,
         i_neck = 1/neck,
         i_chest = 1/chest,
         i_abdomen = 1/abdomen,
         i_hip = 1/hip,
         i_thigh = 1/thigh,
         i_knee = 1/knee,
         i_ankle = 1/ankle,
         i_bicep = 1/bicep) %>% 
  select(-id, -bodyfat_brozek, -body_density, -weight, -neck, -chest, -abdomen,
         -hip, -thigh, -knee, -ankle, -bicep)

```


NOTE: Collinearity continues though. Weight with all others. Just fyi. Not manually removing any covariates as they would be removed during the model selection processes?

## Model Selection

```{r stepwise}
mult.fit = lm(bodyfat_siri ~ ., data = bodyfat_df)

#Backward
step(mult.fit, direction = 'backward')

#Forward
intercept_only = lm(bodyfat_siri ~ 1, data = bodyfat_df)
step(intercept_only, direction = "forward", scope = formula(mult.fit))

#Stepwise
step(mult.fit, direction = 'both')
```

Based on Backward: 6 predictors - age, height, forearm, wrist, i_neck, i_abdomen 
Based on Forward: 6 predictors - age, height, forearm, wrist, i_neck, i_abdomen
Based on Stepwise: 6 predictors - age, height, forearm, wrist, i_neck, i_abdomen



```{r automatic criterion cp}
bodyfat_df =
  bodyfat_df %>%
  select(bodyfat_siri, everything())

mat = as.matrix(bodyfat_df)
# Printing the 2 best models of each size, using the Cp criterion:
leaps(x = mat[,2:14], y = mat[,1], nbest = 2, method = "Cp")
```

```{r automatic criterion adj r^2}
# Printing the 2 best models of each size, using the adjusted Rˆ2 criterion:
leaps(x = mat[,2:14], y = mat[,1], nbest = 2, method = "adjr2")
```

```{r automatic criterion output}
b = regsubsets(bodyfat_siri ~ ., data = bodyfat_df)
rs = summary(b)

par(mfrow = c(1,2))
plot(1:8, rs$cp, xlab = "No of predictors", ylab = "Cp Statistic")
abline(0,1)
plot(1:8, rs$adjr2, xlab = "No of predictors", ylab = "Adj R2")
```

Based on Cp: 6 predictors (age, height, forearm, wrist, i_neck, i_abdomen)

Based on Adj R^2: 8 predictors (age, height, forearm, wrist, i_neck, i_abdomen, i_weight, i_chest)

NOTE: Some of these are highly correlated (DISCUSSION POINT!). Would use shrinkage method (LASSO) which would factor the matter of collinearity into the process). If we were to just abide by this though, we would have to use Vif values etc and drop the super highly correlated covariates. (Must ensure that the predictive ability is retained though by actually fitting the model and keeping track of the adj. r^2 or whatever parameter.)

```{r comparing the two suggested models}
six_pred = lm(bodyfat_siri ~ age + height + forearm + wrist + i_neck + i_abdomen, data = bodyfat_df)
summary(six_pred)

eight_pred = lm(bodyfat_siri ~ age + height + forearm + wrist + 
                  i_neck + i_abdomen + i_weight + i_chest, data = bodyfat_df)
summary(eight_pred)

anova(six_pred, eight_pred)
```

DISCUSSION: Smaller is better. Can discuss anova hypotheses and results as proof.

```{r lasso}
# supply sequence of lambda values for the lasso cross validation for lambda
lambda_seq <- 10^seq(-3, 0, by = .1)
set.seed(2022)

# save matrix of predictors to pass to the lasso function
predictors_dat.state =
  bodyfat_df %>% 
  select(age, height, forearm, wrist, i_weight, i_neck, 
         i_chest, i_abdomen, i_hip, i_thigh, i_knee, i_ankle, i_bicep) %>% 
    as.matrix()

response_dat.state =
  bodyfat_df %>% 
  select(bodyfat_siri) %>% 
  as.matrix()

cv_lasso_fit <- glmnet::cv.glmnet(x = predictors_dat.state,
                                    y = response_dat.state,
                                    lambda = lambda_seq,
                                    nfolds = 10)
cv_lasso_fit
```

Min lambda is 0.07943.

```{r lasso regression}
lasso_fit = glmnet::glmnet(x = predictors_dat.state,
                           y = response_dat.state,
                           lambda = cv_lasso_fit$lambda.min)
coef(lasso_fit)
```

Based on LASSO: 8 predictors (different though) - age, height, forearm, wrist, i_neck, i_abdomen, i_thigh, i_bicep. 

```{r fitting new model}
eight_pred_lasso = lm(bodyfat_siri ~ age + height + forearm + wrist + 
                  i_neck + i_abdomen + i_thigh + i_bicep, data = bodyfat_df)
summary(eight_pred_lasso)
```

DISCUSSION: Adj R^2 only SLIIIIGHTLY better than six_pred model. 
Principle of parsimony? Smaller model is better? Not much predictive capacity is lost.

## Diagnostics

```{r diagnostic plots}
par(mfrow = c(2,2))
plot(six_pred)

par(mfrow = c(2,2))
plot(eight_pred)

par(mfrow = c(2,2))
plot(eight_pred_lasso)
```

Looks good. Super slight differences. For six_pred, things look pretty great.


## Validation

```{r cross validation for six_pred}
set.seed(2022)

# use 10-fold validation and create the training sets
train = trainControl(method = "cv", number = 10)

# fit the 6-variables model that we selected as our final model
model_caret = train(bodyfat_siri ~ age + height + forearm + wrist + i_neck + i_abdomen,
                    data = bodyfat_df,
                    trControl = train,
                    method = 'lm',
                    na.action = na.pass)
                    
                    
model_caret
```


RMSE      Rsquared   MAE     
4.241122  0.7481343  3.460785


```{r cross validation for six_pred final}
model_caret$resample
```

From the output above, the overall RMSE (root mean squared error) is 4.241122.


