---
title: "code_plots_tables"
author: "Tvisha R. Devavarapu"
date: "2022-12-16"
output: github_document
---

# Set Up

```{r libraries set up, message = FALSE}
library(tidyverse)
library(ggplot2)
library(patchwork)
library(GGally)
library(gtsummary)

# https://cran.r-project.org/web/packages/gtsummary/vignettes/tbl_regression.html
# https://education.rstudio.com/blog/2020/07/gtsummary/ 
# https://www.danieldsjoberg.com/gtsummary/reference/add_glance.html 
```

```{r dataset set up}
bodyfat_df = 
  readxl::read_excel("body_density_data.xlsx") %>%
  janitor::clean_names() 

head(bodyfat_df)
```

# Descriptive Stats + Y and X Distributions + Correlations

```{r descriptive stats of variables}
bodyfat_df %>% 
  select(-id, -bodyfat_siri, -bodyfat_brozek) %>% 
  gtsummary::tbl_summary() %>% 
  gtsummary::bold_labels() 
```

```{r Y Distribution (Body Density)}
bodyfat_df %>%
  ggplot(aes(x = body_density)) +
  geom_histogram() +
  labs(x = "Body Density Measurement (in gm/cm^3)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))
```

```{r normality, y-x rels, collinearity in covariates (xs)}
bodyfat_df %>% 
  select(-bodyfat_siri, -bodyfat_brozek, -id) %>% 
  relocate("body_density") %>% 
  ggpairs(., axisLabels = "none")
```

# Transformations

```{r inv_transformation for weight}
before = 
bodyfat_df %>%
  ggplot(aes(x = weight)) +
  geom_histogram() +
  labs(x = "Weight (in lbs)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

after = 
bodyfat_df %>% 
  mutate(inv_weight = 1/(weight)) %>% 
  ggplot(aes(x = inv_weight)) +
  geom_histogram() +
  labs(x = "Inverse Weight (1/Weight)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

before + after
```

```{r inv_transformation for all other transformed variables}
before2 = 
bodyfat_df %>%
  ggplot(aes(x = neck)) +
  geom_histogram() +
  labs(x = "Neck Circumference (in cm)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

after2 = 
bodyfat_df %>% 
  mutate(inv_neck = 1/(neck)) %>% 
  ggplot(aes(x = inv_neck)) +
  geom_histogram() +
  labs(x = "Inverse Neck (1/Neck)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

neck = before2 + after2

before3 = 
bodyfat_df %>%
  ggplot(aes(x = chest)) +
  geom_histogram() +
  labs(x = "Chest Circumference (in cm)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

after3 = 
bodyfat_df %>% 
  mutate(inv_chest = 1/(chest)) %>% 
  ggplot(aes(x = inv_chest)) +
  geom_histogram() +
  labs(x = "Inverse Chest (1/Chest)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

chest = before3 + after3

before4 = 
bodyfat_df %>%
  ggplot(aes(x = abdomen)) +
  geom_histogram() +
  labs(x = "Abdomen Circumference (in cm)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

after4 = 
bodyfat_df %>% 
  mutate(inv_abdomen = 1/(abdomen)) %>% 
  ggplot(aes(x = inv_abdomen)) +
  geom_histogram() +
  labs(x = "Inverse Abdomen (1/Abdomen)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

abdomen = before4 + after4

before5 = 
bodyfat_df %>%
  ggplot(aes(x = hip)) +
  geom_histogram() +
  labs(x = "Hip Circumference (in cm)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

after5 = 
bodyfat_df %>% 
  mutate(inv_hip = 1/(hip)) %>% 
  ggplot(aes(x = inv_hip)) +
  geom_histogram() +
  labs(x = "Inverse Hip (1/Hip)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

hip = before5 + after5

before6 = 
bodyfat_df %>%
  ggplot(aes(x = thigh)) +
  geom_histogram() +
  labs(x = "Thigh Circumference (in cm)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

after6 = 
bodyfat_df %>% 
  mutate(inv_thigh = 1/(thigh)) %>% 
  ggplot(aes(x = inv_thigh)) +
  geom_histogram() +
  labs(x = "Inverse Thigh (1/Chest)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

thigh = before6 + after6

before7 = 
bodyfat_df %>%
  ggplot(aes(x = knee)) +
  geom_histogram() +
  labs(x = "Knee Circumference (in cm)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

after7 = 
bodyfat_df %>% 
  mutate(inv_knee = 1/(knee)) %>% 
  ggplot(aes(x = inv_knee)) +
  geom_histogram() +
  labs(x = "Inverse Knee (1/Knee)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

knee = before7 + after7

before8 = 
bodyfat_df %>%
  ggplot(aes(x = ankle)) +
  geom_histogram() +
  labs(x = "Ankle Circumference (in cm)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

after8 = 
bodyfat_df %>% 
  mutate(inv_ankle = 1/(ankle)) %>% 
  ggplot(aes(x = inv_ankle)) +
  geom_histogram() +
  labs(x = "Inverse Ankle (1/Ankle)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

ankle = before8 + after8

before9 = 
bodyfat_df %>%
  ggplot(aes(x = bicep)) +
  geom_histogram() +
  labs(x = "Bicep Circumference (in cm)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

after9 = 
bodyfat_df %>% 
  mutate(inv_bicep = 1/(bicep)) %>% 
  ggplot(aes(x = inv_bicep)) +
  geom_histogram() +
  labs(x = "Inverse Bicep (1/Chest)",
       y = "Counts") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 70, hjust = 1))

bicep = before9 + after9
```

```{r inverse transforms}
bodyfat_df = 
  bodyfat_df %>%
  mutate(i_weight = 1/weight,
         i_neck = 1/neck,
         i_chest = 1/chest,
         i_abdomen = 1/abdomen,
         i_hip = 1/hip,
         i_thigh = 1/thigh,
         i_knee = 1/knee,
         i_ankle = 1/ankle,
         i_bicep = 1/bicep) %>% 
  select(-id, -bodyfat_siri, -bodyfat_brozek, -weight, -neck, -chest, -abdomen,
         -hip, -thigh, -knee, -ankle, -bicep)

```

```{r TRANSFORMED normality, y-x rels, collinearity in covariates (xs)}
bodyfat_df %>% 
  relocate("body_density") %>% 
  ggpairs(., axisLabels = "none")
```

# Model Selection

## Stepwise

```{r stepwise}
mult.fit = lm(body_density ~ ., data = bodyfat_df)

#Backward
step(mult.fit, direction = 'backward')

#Forward
intercept_only = lm(body_density ~ 1, data = bodyfat_df)
step(intercept_only, direction = "forward", scope = formula(mult.fit))

#Stepwise
step(mult.fit, direction = 'both')
```

Based on Backward: 8 predictors - age, height, wrist, i_neck, i_abdomen, i_chest, i_weight, i_bicep 
Based on Forward: 6 predictors - age, height, i_bicep, wrist, i_neck, i_abdomen
Based on Stepwise: 8 predictors - age, height, wrist, i_neck, i_abdomen, i_chest, i_weight, i_bicep

```{r fitting models stepwise}
six_pred = lm(body_density ~ age + height + i_bicep + wrist + i_neck + i_abdomen, data = bodyfat_df)
summary(six_pred)

eight_pred = lm(body_density ~ age + height + wrist + i_neck + i_abdomen + i_chest + i_weight + i_bicep, 
                data = bodyfat_df)
summary(eight_pred)

```

```{r stepwise regression tables}
# Six Pred
a = 
tbl_regression(six_pred, intercept = TRUE, estimate_fun = ~style_sigfig(., digits = 5)) %>% 
  modify_column_unhide(column = std.error) %>%
  add_glance_table(include = c("r.squared", "adj.r.squared", "AIC")) %>% 
  add_significance_stars() %>% 
  add_vif() %>% 
  bold_labels()

# Eight Pred
b = 
tbl_regression(eight_pred, intercept = TRUE, estimate_fun = ~style_sigfig(., digits = 5)) %>% 
  modify_column_unhide(column = std.error) %>%
  add_glance_table(include = c("r.squared", "adj.r.squared", "AIC")) %>% 
  add_significance_stars() %>% 
  add_vif() %>% 
  bold_labels()

```

## Automatic

```{r automatic criterion cp}
bodyfat_df =
  bodyfat_df %>%
  select(body_density, everything())

mat = as.matrix(bodyfat_df)
# Printing the 2 best models of each size, using the Cp criterion:
leaps(x = mat[,2:14], y = mat[,1], nbest = 2, method = "Cp")
```

```{r automatic criterion adj r^2}
# Printing the 2 best models of each size, using the adjusted Rˆ2 criterion:
leaps(x = mat[,2:14], y = mat[,1], nbest = 2, method = "adjr2")
```

```{r automatic criterion output}
b = regsubsets(body_density ~ ., data = bodyfat_df)
rs = summary(b)

par(mfrow = c(1,2))
plot(1:8, rs$cp, xlab = "No. of predictors", ylab = "Cp Statistic")
abline(0,1)
plot(1:8, rs$adjr2, xlab = "No. of predictors", ylab = "Adj R2")

rs
```

Based on Cp and Adj R^2: Same 8 predictors (age height forearm wrist i_weight i_neck i_chest i_abdomen)

```{r fitting suggested auto models}
eight_pred_auto = lm(body_density ~ age + height + wrist + i_neck + i_abdomen + i_chest + i_weight + forearm, 
                data = bodyfat_df)
summary(eight_pred_auto)
```

```{r automatic regression table}
# Eight Pred Auto
c = 
tbl_regression(eight_pred_auto, intercept = TRUE, estimate_fun = ~style_sigfig(., digits = 5)) %>% 
  modify_column_unhide(column = std.error) %>%
  add_glance_table(include = c("r.squared", "adj.r.squared", "AIC")) %>% 
  add_significance_stars() %>% 
  add_vif() %>% 
  bold_labels()

```

## Lasso

```{r lasso}
# supply sequence of lambda values for the lasso cross validation for lambda
lambda_seq <- 10^seq(-3, 0, by = .1)
set.seed(2022)

# save matrix of predictors to pass to the lasso function
predictors_dat.state =
  bodyfat_df %>% 
  select(age, height, forearm, wrist, i_weight, i_neck, 
         i_chest, i_abdomen, i_hip, i_thigh, i_knee, i_ankle, i_bicep) %>% 
    as.matrix()

response_dat.state =
  bodyfat_df %>% 
  select(body_density) %>% 
  as.matrix()

cv_lasso_fit <- glmnet::cv.glmnet(x = predictors_dat.state,
                                    y = response_dat.state,
                                    lambda = lambda_seq,
                                    nfolds = 10)
cv_lasso_fit
```

```{r lasso regression}
lasso_fit = glmnet::glmnet(x = predictors_dat.state,
                           y = response_dat.state,
                           lambda = cv_lasso_fit$lambda.min)
coef(lasso_fit)
```

```{r fitting lasso model}
four_pred_lasso = lm(body_density ~ age + height + wrist + i_abdomen, 
                      data = bodyfat_df)
summary(four_pred_lasso)
```

```{r lasso regression table}
# Four Pred Lasso
d = 
tbl_regression(four_pred_lasso, intercept = TRUE, estimate_fun = ~style_sigfig(., digits = 5)) %>% 
  modify_column_unhide(column = std.error) %>%
  add_glance_table(include = c("r.squared", "adj.r.squared", "AIC")) %>% 
  add_significance_stars() %>% 
  add_vif() %>% 
  bold_labels()

```

# Regression Tables

```{r JOINT REGRESSION TABLE}
tbl_merge(tbls = list(a, b, c, d),
          tab_spanner = c("**Forward**", "**Backward & Stepwise**", 
                          "**Cp and Adj R^2**", "**Lasso**")) %>%
  modify_table_body(~.x %>% arrange(row_type == "glance_statistic"))
```

```{r INDIVIDUAL MODELS for APPENDIX}

# Six Pred
tbl_regression(six_pred, intercept = TRUE, estimate_fun = ~style_sigfig(., digits = 5)) %>% 
  modify_column_unhide(column = std.error) %>%
  add_glance_table(include = c("r.squared", "adj.r.squared", "AIC")) %>%
  add_vif() %>% 
  bold_labels()

# Eight Pred
tbl_regression(eight_pred, intercept = TRUE, estimate_fun = ~style_sigfig(., digits = 5)) %>% 
  modify_column_unhide(column = std.error) %>%
  add_glance_table(include = c("r.squared", "adj.r.squared", "AIC")) %>%
  add_vif() %>% 
  bold_labels()

# Eight Pred Auto
tbl_regression(eight_pred_auto, intercept = TRUE, estimate_fun = ~style_sigfig(., digits = 5)) %>% 
  modify_column_unhide(column = std.error) %>%
  add_glance_table(include = c("r.squared", "adj.r.squared", "AIC")) %>%
  add_vif() %>% 
  bold_labels()

# Four Pred Lasso
tbl_regression(four_pred_lasso, intercept = TRUE, estimate_fun = ~style_sigfig(., digits = 5)) %>% 
  modify_column_unhide(column = std.error) %>%
  add_glance_table(include = c("r.squared", "adj.r.squared", "AIC")) %>%
  add_vif() %>% 
  bold_labels()
```

# Diagnostic Plots

```{r diagnostic plots}
par(mfrow = c(2,2))
plot(six_pred)

par(mfrow = c(2,2))
plot(eight_pred)

par(mfrow = c(2,2))
plot(eight_pred_auto)

par(mfrow = c(2,2))
plot(four_pred_lasso)
```

# RMSE Plot - Cross Validation

```{r rmse_plot}
set.seed(2022)

#a new id column
cv_bodyfat = bodyfat_df %>% mutate(id = row_number()) %>% relocate(id)


train_df = sample_n(cv_bodyfat, 80)
test_df = anti_join(cv_bodyfat, train_df, by = "id")

cv_df = 
  crossv_mc(cv_bodyfat, 100) 

cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    four_pred_mod = map(train, ~lm(body_density ~ age + height + wrist + i_abdomen, 
                                   data = .x)),
    six_pred_mod = map(train, ~lm(body_density ~ age + height + i_bicep + wrist + 
                                    i_neck + i_abdomen, data = .x)),
    eight_pred_mod_stepwise = map(train, ~lm(body_density ~ age + height + wrist + i_neck + 
                                      i_abdomen + i_chest + i_weight + i_bicep, 
                                    data = .x)),
    eight_pred_mod_criterion = map(train, ~lm(body_density ~ age + height + forearm + wrist +
                                           i_weight + i_neck + i_chest + i_abdomen, 
                                    data = .x))) %>% 
  mutate(
    rmse_lasso = map2_dbl(four_pred_mod, test, ~rmse(model = .x, data = .y)),
    rmse_forward = map2_dbl(six_pred_mod, test, ~rmse(model = .x, data = .y)),
    rmse_backward_stepwise = map2_dbl(eight_pred_mod_stepwise, test, ~rmse(model = .x, 
                                                                        data = .y)),
    rmse_automatic = map2_dbl(eight_pred_mod_criterion, test, ~rmse(model = .x, 
                                                                        data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```




